---
title: "**View the Dataset**"
page-layout: full
---

Explore the Coe College Tree Archive data online through this interactive table. To use the interactive table, try:

-   Scrolling across to see all columns in the table

-   Filtering the observations by entering key words into the search box

-   Sorting observations by column value using the arrows by the column name

For additional details on the columns in the interactive table, consult the [data dictionary](https://github.com/CoeTreeArchive/CoeTreeArchive.github.io/raw/main/documentation/data-dictionary.xlsx).

<br>

```{r, results='hide'}
#| error: false
#| echo: false
#| message: false
#| warning: false

#:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
## Set-Up ----------------------------------------------------------------------
#:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# All packages needed
my_packages <- c(
  'tidyverse',
  'openxlsx',
  'DT'
)

# Install any packages not already installed
new_packages <- my_packages[!(my_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)){
  install.packages(new_packages)
}

# Library all packages
lapply(my_packages, library, character.only = TRUE)

# Reduce scientific notation
options(scipen = 9)

# Remove unnecessary objects
rm(new_packages, my_packages)

# Read in the dataset
df <- read.xlsx('../data/coe-tree-archive-all-years.xlsx', detectDates = T)
```

```{r}
#| error: false
#| echo: false
#| message: false
#| warning: false

df <- df %>% 
  select(-c('Special.Notes')) %>% 
  mutate(
    Tree.ID = paste(
      '<a href="https://coetreearchive.github.io/tree-profiles/tree_', Tree.ID, 
      '.html"> ', Tree.ID, '<a/>', sep = '')
  )

datatable(df, rownames = FALSE, escape = FALSE)
```
